The landscape of chloroplast genome assembly tools

### 2019-06-09 manuscript/bmc_article.tex
Update on Overleaf.

>>>>

\section*{Availability of data and materials}
The supplemental material is available from Zenodo \cite{zenodosupplement}. The simulated data set is available from Zenodo \cite{zenododataset}. All program code is available via Zenodo \cite{zenodorepo} or from Github \cite{github-benchmark-repo}. The input data sets can be generated using the raw reads from NCBI SRA (links for each data set in \cref{tab:real_dataset_details}). The resulting assemblies are avaiable from Zenodo \cite{zenodoassemblies}.
